---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# scRobustPCA

Performs robust PCA with modified PCs on Seurat objects for scRNA-Seq dimensionality reduction.

## Installation

You can install scRobustPCA from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("gmstanle/scRobustPCA")
```

# Working example on 80 PBMCs
Intended only to demonstrate a functional workflow.
`pbmc_small` is a subsetted dataset with 80 cells and 230 genes 
included in the `Seurat` package.


## Calculate rPCA
```{r example}
require(Seurat)
require(scRobustPCA)
pcs.use=1:5
pbmc_small <- FindVariableGenes(pbmc_small, do.plot = F) # optional
pbmc_small <- RunRobPCA(pbmc_small, npcs=max(pcs.use), use.modified.pcscores = T)
```

## Plot pairwise combinations of PCs
```{r}
pairs(GetCellEmbeddings(pbmc_small, reduction.type = 'rpca'))
```

## Calculate TSNE
```{r}
pbmc_small <- RunTSNE(pbmc_small, reduction.use = 'rpca', dims.use = pcs.use,perplexity=10)
```

## Cluster cells
Note: need to set the dims.use parameter or `FindClusters` seems to default to using `'pca'` dimensionality reduction. 
```{r}

pbmc_small <- FindClusters(pbmc_small, reduction.type = 'rpca', dims.use = pcs.use, print.output = F)
TSNEPlot(pbmc_small)
```


